\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontspec}
\setmainfont[Numbers=OldStyle]{Linux Libertine}
%disable Linux Libertine Semibold
\newfontfamily\fixedwidth{Courier}

\def \Name  {Wentao Liu}
\def \Phone {+86 182-0026-0891}
\def \Email {wentao.liu.zero@gmail.com}

\hypersetup{
	colorlinks,
	breaklinks,
	linkcolor = black,
	urlcolor  = blue,
	anchorcolor = black,
	citecolor   = black,
	pdftitle  = {CV - \Name},
	pdfauthor = {\Name}
}

\setlength{\textwidth}{5.1in} % Text width of the document
\setlist[itemize]{leftmargin=*, label={-}, topsep=1pt}

\begin{document}
\sloppy

\hspace*{-\sectionwidth}{\LARGE \scshape \Name}

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

{\vspace*{-1.2em}}
\hspace*{-\sectionwidth}{\hspace*{-0.2em}}{
	{\href {mailto:\Email}{\texttt \Email}}
	{\hspace*{0.5em}}
	|
	{\hspace*{0.5em}}
	{\texttt \Phone}
}

{\vspace*{-2.0em}}
\begin{resume}
\section{Education}

{\bf M.Sc.}, Computer Science \hfill Sept. 2015 - (expected) Jun. 2018\\
Sichuan University \hfill Chengdu

{\bf B.Eng.}, Software Engineering \hfill Sept. 2011 - Jun. 2015\\
Sichuan University \hfill Chengdu

\section{Employment}

\def \HAXMlink {\href {https://software.intel.com/en-us/android/articles/intel-hardware-accelerated-execution-manager} {Intel{\textregistered} HAXM}}

{\bf GPU Arch Intern} \hfill Mar. 2017 - present\\
NVIDIA SMart Arch Team \hfill Shanghai\\
{\fixedwidth\{C++, Python, Bash, Perl\}}

\begin{itemize}
	\item[-] {Develop stream multiprocessor SMart for Turing architecture}
	\item[-] {Branch SMart CUDA lib from Volta architecture to Turing architecture}
	\item[-] {Help deliver traces for Volta/Turing architecture}
	\item[-] {Automate traces comparing/refreshing with Python script}
\end{itemize}

{\bf Engineering Intern} \hfill Sept. 2016 - Feb. 2017\\
Intel Open Source Technology Center \hfill Beijing\\
{\fixedwidth\{C++, Bash, Python, git\}}

\begin{itemize}
	\item{Develop {\HAXMlink}}, help release HAXM 6.0.6, 6.1.0
	\item{Port HAXM to QEMU upstream that enhance QEMU performance}
	\item{Maintain AOSP (Android Open Source Project) continuous integration workflow}
\end{itemize}

\section{Technical}

Functional Programming

\begin{itemize}
	\item{Solution to {\it University of Pennsylvania CIS 194: Introduction to Haskell} \\
	{\fixedwidth\{Haskell\}} \hfill \url{https://github.com/WentaoZero/UPenn-CIS-194-2015}}
	\item{Solution to {\it Structure and Interpretation of Computer Programs}\\
	{\fixedwidth\{Lisp\}} \hfill \url{https://github.com/WentaoZero/SICP-Solution}}
\end{itemize}

GPU Programming \& Parallel Programming

\begin{itemize}
	\item{Solution to {\it Udacity CS 344: Intro to Parallel Programming} \\
	{\fixedwidth\{CUDA\}} \hfill \url{https://github.com/WentaoZero/Intro-to-Parallel-Programming}}
\end{itemize}

Programming Language \& Tool

\begin{itemize}
\item{\fixedwidth Python, Lisp, Haskell, C, C++, CUDA}
\item{\fixedwidth Unix shell, git, Vim}
\end{itemize}

\section{Misc.}

GitHub \hfill {\url{https://github.com/WentaoZero}}

{\vspace*{-0.5em}}

Stack Overflow \hfill {\url{https://stackoverflow.com/users/3853711/Wentao}}

\end{resume}

\end{document}
