\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
%\usepackage{times}

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{marvosym}
\usepackage{xeCJK}

\setmainfont{Adobe Garamond}

\hypersetup{colorlinks, breaklinks, linkcolor=black, urlcolor=blue, anchorcolor=black, citecolor=black}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

\def \Email {wentao.liu.zero@gmail.com}
\def \Name  {WENTAO LIU}
\def \Phone {+(86) 182-0026-0891}

\def \HEADER {
	\moveleft.5\hoffset\centerline{\LARGE \bf \Name} % Your name at the top
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
	\moveleft.5\hoffset\centerline{{\Phone} {\hspace*{0.0em}} {\href {mailto:\Email}{\underline{\smash{\Email}}}}}
}

\def \WentaoResume
{
	\HEADER

	\begin{resume}

	\def \ItemVindent {\vspace*{-0.7em}}

	\section{EDUCATION}

	{\bf M.Sc.}, Computer Science, {\bf Sichuan University} \hspace*{\fill} Sept. 2015 - (expected) Jun. 2018

	{\ItemVindent}

	{\bf B.Eng.}, Software Engineering, {\bf Sichuan University} \hspace*{\fill} Sept. 2011 - Jun. 2015

	\section{EXPERIENCE}

	\def \HAXMlink {\href {https://software.intel.com/en-us/android/articles/intel-hardware-accelerated-execution-manager} {\underline{\smash{Intel® HAXM}}}}
	\def \QEMUlink {\href {http://wiki.qemu.org} {\underline{\smash{QEMU}}}}
	\def \AOSPlink {\href {https://source.android.com} {\underline{\smash{AOSP}}}}

	Engineering Intern at {\bf Intel OTC}, Beijing
	\hspace*{\fill}
	Sept. 2016 - Feb. 2017\\
	(Intel Open Source Technology Center)
	\begin{itemize}[leftmargin=*, topsep=1pt]
		\item[-] {Port {\HAXMlink} to {\QEMUlink} upstream and maintain}
		\item[-] {Help release {\HAXMlink} 6.0.6, 6.1.0}
		\item[-] {Maintain {\AOSPlink} (Android Open Source Project) continuous integration workflow}
	\end{itemize}

	\section{TECHNICAL}

	\def \CUDAlink {https://github.com/WentaoZero/Intro-to-Parallel-Programming}

	GPU Programming \& Parallel Programming
	\begin{itemize}[leftmargin=*, topsep=1pt]
		\item[-] Solution to {\it Udacity CS 344: Intro to Parallel Programming} \\
		({\bf CUDA}, C) \hspace*{\fill} \href {\CUDAlink} {\underline {\smash {\CUDAlink}}}
	\end{itemize}

	\def \UPennHSlink {https://github.com/WentaoZero/UPenn-CIS-194-2015}
	\def \HasLink {https://github.com/WentaoZero/Programming-in-Haskell}

	Functional Programming
	\begin{itemize}[leftmargin=*, topsep=1pt]
		\item[-] Solution to {\it University of Pennsylvania CIS 194: Introduction to Haskell} \\
		({\bf Haskell}) \hspace*{\fill} \href {\UPennHSlink} {\underline {\smash {\UPennHSlink}}}
		\item[-] Solution to {\it Programming in Haskell} \\
		({\bf Haskell}) \hspace*{\fill} \href {\HasLink} {\underline {\smash {\HasLink}}}
	\end{itemize}

	Extra
	\begin{itemize}[leftmargin=*, topsep=1pt]
		\item[-] {Python, Lisp, Git, Unix shell}
	\end{itemize}

	\section{MEDIA}

	\def \GitHubLink {https://github.com/WentaoZero}
	\def \StackOverflowLink {http://stackoverflow.com/users/3853711/Wentao}
	\def \LinkedinLink {https://www.linkedin.com/in/WentaoZero}

	GitHub \hspace*{\fill} {\href {\GitHubLink} {\underline {\smash {\GitHubLink}}}}

	{\ItemVindent}
	StackOverflow \hspace*{\fill} {\href {\StackOverflowLink} {\underline {\smash {\StackOverflowLink}}}}

	{\ItemVindent}
	Linkedin \hspace*{\fill} {\href {\LinkedinLink} {\underline {\smash {\LinkedinLink}}}}

	\end{resume}
}

\WentaoResume

\end{document}
